An Axiomatic Basis for Computer Programming: Review

### 2017-02-14 hoare/paper.tex
Add quadratic equation

For example lets take task on finding real roots for quadratic equation.

We limits input set according to discriminant and set of real numbers in
predicate P. Then we could find values by some program Q. And finally check
whether equation holds or not in R.

>>>>

For example lets take task on finding real roots for quadratic equation:
$$ ax^2 + bx + c = 0$$

We limits input domain as set of real numbers and according to discriminant in
predicate P:
$$ P \equiv (a, b, c \in \mathbb{R}) \wedge (b^2 - 4ac \geq 0)$$

Then we could find values by some program Q. And finally check
whether equation holds or not in R.
